---
title: "p8105_hw5_sc5126"
author: "Si Chen"
date: "`r Sys.Date()`"
output: github_document
---

**Load library** 
```{r load_library, warning = FALSE, message = FALSE}
library(tidyr)
library(tidyverse)
library(rvest)
library(dplyr)
library(cowplot)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```



## Problem 2

```{r import & clean data, warning = FALSE}
# This zip file contains data from a longitudinal study that included a control arm and an experimental arm.
# Data for each participant is included in a separate file, and file names include the subject ID and arm.

# Start with a dataframe containing all file names; the list.files function will help
# Iterate over file names and read in data for each subject using purrr::map 
# and saving the result as a new variable in the dataframe

df = 
  list.files("data/problem2", full.names = TRUE) %>% 
  as.tibble() %>% 
  rename(path = value) %>% 
  mutate(
    data = map(path, read_csv)
  ) %>% 
  unnest()

```


```{r tidy_data}
# Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time
# Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary

tidy_df = 
  df %>% 
  mutate(
    arm = str_sub(path, -10, -8),
    id = str_sub(path, -10, -5)
    ) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "observation",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(id, arm, week, observation)

```


```{r spaghetti plot}
# Make a spaghetti plot showing observations on each subject over time, 
# and comment on differences between groups.

tidy_df %>% 
  ggplot(aes(x = week, y = observation, group = id, colour = arm)) +
  geom_line() +
#  facet_grid(~arm)+
  xlab("Week") + 
  ylab("Observation value") +
  labs(color = "Group")+
  ggtitle("Observations on each subject over time")

```
We can see that the subjects in the experiment group generally have higher observation values than those in the control group. The observations from the experiment group are exhibiting an increasing trend while those from the control group remain relatively stable overtime. 



## Problem 3

```{r sim_function}
# When designing an experiment or analysis, 
# a common question is whether it is likely that a true effect will be detected – 
# put differently, whether a false null hypothesis will be rejected. 
# The probability that a false null hypothesis is rejected is referred to as power, 
# and it depends on several factors, including: the sample size; the effect size; and the error variance. 
# In this problem, you will conduct a simulation to explore power in a one-sample t-test.

# First set the following design elements:
# Fix n=30
# Fix σ=5
# Set μ=0. Generate 5000 datasets from the model x∼Normal[μ,σ]

# For each dataset, save μ^ and the p-value arising from a test of H:μ=0
# using α=0.05. Hint: to obtain the estimate and p-value, use broom::tidy to clean the output of t.test.

set.seed(1)


sim_test_fn = function(n=30, mu, sigma=5){
  
  sim_data = tibble(rnorm(n = n, mean = mu, sd = sigma))
  
  sim_data %>% 
    t.test() %>% 
    broom::tidy() %>% 
    select(estimate, p.value)
}

```

```{r simulate_result}
# Repeat the above for μ={1,2,3,4,5,6}, and complete the following:

sim_result_df = 
  expand_grid(
    mu = c(0:6),
    iter = 1:5000
    ) %>%
  mutate(
    estimate_df = map(mu, ~sim_test_fn(mu=.x))
  ) %>%
  unnest(estimate_df) %>% 
  mutate(
    reject = ifelse(p.value < 0.05, 1, 0)
    )

```

```{r plot_power}
# Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. Describe the association between effect size and power.

sim_result_df %>%  
  group_by(mu) %>% 
  summarise(
    n_reject = sum(reject==1),
    n_obs = n()
    ) %>%  
  ggplot(aes(x=mu, y = n_reject/n_obs)) +
  geom_line() +
  labs(
    title = "Effect size and power association",
    x = "True value of mean",
    y = "Power") 

```

```{r plot_avg_estimate}
# Make a plot showing the average estimate of μ^ on the y axis and the true value of μ on the x axis. 

p1 = 
  sim_result_df %>%  
  group_by(mu) %>% 
  summarise(
    avg_estimate = mean(estimate),
    ) %>%  
  ggplot(aes(x=mu, y = avg_estimate)) +
  geom_line() +
  labs(
    title = "Average estimate of μ VS True value of μ",
    x = "True value of mean",
    y = "Average estimate of mean") 

# Make a second plot (or overlay on the first) 
# the average estimate of μ^ only in samples for which the null was rejected on the y axis 
# and the true value of μ on the x axis. 

p2 = 
  sim_result_df %>% 
  filter(reject == 1) %>% 
  group_by(mu) %>% 
  summarise(
    avg_estimate = mean(estimate),
    ) %>%  
  ggplot(aes(x=mu, y = avg_estimate)) +
  geom_line() +
  labs(
    title = "Null rejected: Avg estimate of μ VS True value of μ",
    x = "True value of mean",
    y = "Average estimate of mean for rejected null") 


```

```{r show_plot}
# Is the sample average of μ^ across tests for which 
# the null is rejected approximately equal to the true value of μ? Why or why not?

plot_grid(p1, p2, ncol=2)

```
They are not equal. From the plots we can see that when the null hypothesis is rejected and the true mean is between 0 and 3, the sample average of estimated mean is higher than the true mean. In addition, since the null hypothesis is rejected, it means that the sample mean differs from the true mean.


