---
title: "p8105_hw5_sc5126"
author: "Si Chen"
date: "`r Sys.Date()`"
output: github_document
---

**Load library** 
```{r load_library, warning = FALSE, message = FALSE}
library(tidyr)
library(tidyverse)
library(rvest)
library(dplyr)


knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

```{r import data,  warning = FALSE}
# Describe the raw data. Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

hom_df = 
  read_csv("data/homicide-data.csv", show_col_types = FALSE) %>% 
  janitor::clean_names() %>% 
  mutate(
    city_state = str_c(city, ",", state), # Create a city_state variable (e.g. “Baltimore, MD”)
    victim_age = as.numeric(victim_age)
      ) %>% 
  as.tibble()
```

**Raw Data Description**


The data set contains `r ncol(hom_df)` columns and `r nrow(hom_df)` rows. The variables include uni, date of report `reported_date`, basic demographic information (last name `victim_last`, first name `victim_first`, race `victim_race`, age `victim_age`, sex of victim `victim_sex`), location variables (latitude `lat` and longtitude `lon`), the cities and states where the selected police departments are (`city`, `state`), and case status `disposition` given by the `r n_distinct(hom_df$city)` selected American cities from `r n_distinct(hom_df$state)` states.


```{r}
# summarize within cities the total number of homicides

hom_df %>% 
  group_by(city_state) %>% 
  summarise(n_obs = n())

```


```{r }
# summarize within cities the total number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

hom_df %>% 
  filter(disposition == "Closed without arrest" || disposition == "Open/No arrest") %>% 
  group_by(city_state) %>% 
  summarise(n_obs = n())

```


## Problem 2

```{r import & clean data, warning = FALSE}
# This zip file contains data from a longitudinal study that included a control arm and an experimental arm.
# Data for each participant is included in a separate file, and file names include the subject ID and arm.

df = 
  list.files("data/problem2", full.names = TRUE) %>% 
  as.tibble() %>% 
  rename(path = value) %>% 
  mutate(
    data = map(path, read_csv)
  ) %>% 
  unnest()

```


```{r tidy_data}
# Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:
tidy_df = 
  df %>% 
  mutate(
    arm = str_sub(path, -10, -8),
    id = str_sub(path, -10, -5)
    ) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "observation",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(id, arm, week, observation)

```


```{r}
# Start with a dataframe containing all file names; the list.files function will help
# Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe

```


```{r}
# Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
# Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

